---
title: 'Portfolio Manager Report: `r TRADING.PARTY`'
date: "`r format(Sys.Date(), '%B %Y')`"
fontsize: 12pt
output:
  pdf_document:
    fig_height: 3.2
    fig_width: 8
    number_section: yes
    toc: yes
header-includes:
- \usepackage{titling}
- \pretitle{\begin{center}\LARGE\includegraphics[width=24cm]{mosl_title.png}\\[\bigskipamount]}
- \posttitle{\end{center}}
- \usepackage{xcolor}
- \usepackage{color}
- \usepackage{fancyhdr}
- \usepackage{graphicx}
- \usepackage{eurosym}
- \usepackage{longtable}
- \usepackage{booktabs}
- \usepackage{makecell}
- \usepackage{pdflscape}
- \usepackage{multirow}
- \pagestyle{fancy}
- \fancyhf{}
- \lfoot{MOSL Portfolio Manager Report}
- \rhead{\includegraphics[width=6cm]{mosl_header.png}}
- \rfoot{Page \thepage}
classoption: table
---

\newpage

```{r message=FALSE, echo=FALSE, error=FALSE, warning=FALSE}

# Filtering each data set for the Trading Party and creating TEMP file for the rest of the loop --------------------------------------------------------------------------------------------------------------------------------------------------------------------

mps_list_pr <- c("MPS 1", "MPS 2", "MPS 3", "MPS 4", "MPS 7", "MPS 12", "MPS 15", "MPS 16", "MPS 17")

mps_data_temp <- mps_data %>% 
  filter(Trading.Party.ID == TRADING.PARTY) %>%
  droplevels()

mps_list <- unique(mps_data_temp$MPS)

mps_data_melt_temp <- mps_data_melt %>%
  filter(Trading.Party.ID == TRADING.PARTY) %>%
  droplevels()




charges_graph_temp <- charges_graph %>%
  filter(Trading.Party.ID == TRADING.PARTY)

charges_table_temp <- charges_table %>%
  filter(Trading.Party.ID == TRADING.PARTY) %>%
  select(Date, MPS, Charges) %>%
  spread(MPS, Charges)

charges_table_temp$Total <- charges_table_temp %>%
  select(-Date) %>%
  rowSums(na.rm = TRUE)


iprp_status_temp <- iprp_status %>%
  filter(Trading.Party.ID == TRADING.PARTY, Date == latest_period) %>%
  mutate(Date = format(Date, "%Y-%m")) %>%
  select(-Trading.Party.ID)

if (nrow(iprp_status_temp) > 0) {
  
  IPRP_list <- iprp_status_temp$MPS %>%
  droplevels()
  
  IPRP_plans_melt_temp <- IPRP_plans_melt %>%
    filter(Trading.Party.ID == TRADING.PARTY) %>%
  droplevels()
  
}



tracking_pfm_mpsperf_temp <- tracking_pfm_mpsperf %>%
  filter(Trading.Party.ID == TRADING.PARTY) %>%
  select(-Trading.Party.ID)

tracking_pfm_mile_temp <- tracking_pfm_mile %>%
  filter(Trading.Party.ID == TRADING.PARTY) %>%
  select(-Trading.Party.ID)

tracking_performance_temp <- tracking_performance %>% 
  filter(Trading.Party.ID == TRADING.PARTY) %>%
  select(-Trading.Party.ID)

tracking_milestone_temp <- tracking_milestone %>% 
  filter(Trading.Party.ID == TRADING.PARTY) %>%
  select(-Trading.Party.ID)

tracking_watch_temp <- tracking_watch %>%
  filter(Trading.Party.ID == TRADING.PARTY)


mps_summary_mean_temp <- mps_summary %>%
  select(Date, MPS, MPS_Mean) %>%
  filter(MPS %in% (mps_list)) %>%
  spread(MPS, MPS_Mean)

mps_summary_median_temp <- mps_summary %>%
  select(Date, MPS, MPS_Median) %>%
  filter(MPS %in% (mps_list)) %>%
  spread(MPS, MPS_Median)

mps_summary_tasks_temp <- mps_summary %>%
  select(Date, MPS, TotalTaskVolume) %>%
  filter(MPS %in% (mps_list)) %>%
  spread(MPS, TotalTaskVolume)




ops_data_temp <- ops_data %>%
  filter(Trading.Party.ID == TRADING.PARTY)

if (nrow(ops_data_temp) > 0) {
  
  ops_list <- unique(ops_data_temp$OPS)
  
  ops_summary_mean_temp <- ops_summary %>%
  select(Date, OPS, OPS_Mean) %>%
  filter(OPS %in% (ops_list)) %>%
  spread(Date, OPS_Mean)

  ops_summary_median_temp <- ops_summary %>%
    select(Date, OPS, OPS_Median) %>%
    filter(OPS %in% (ops_list)) %>%
    spread(Date, OPS_Median)
  
  ops_summary_tasks_temp <- ops_summary %>%
    select(Date, OPS, TotalTaskVolume) %>%
    filter(OPS %in% (ops_list)) %>%
    spread(Date, TotalTaskVolume)
  
  ops_data_melt_temp <- ops_data_melt %>%
    filter(Trading.Party.ID == TRADING.PARTY) %>%
    droplevels()
  
}

```

# Trading Party MPS Performance

## Charges

```{r message=FALSE, echo=FALSE, error=FALSE, warning=FALSE, fig.width=8, fig.height=10}

# Creating table of charges by MPS --------------------------------------------------------------------------------------------------------------------------------------------------------------------

kable (charges_table_temp, 
       format = "latex", 
       caption = "Breakdown of Charges by MPS", 
       booktabs = TRUE, 
       linesep = "",
       format.args = list(big.mark = ",")
       ) %>%
  kable_styling(
    latex_options = c("repeat_header", "hold_position",
                      "striped", "scale_down", 
                      position = "center", full_width = TRUE)) %>%
  row_spec(0, bold = TRUE)


# Creating two charges graphs and combines as single plot --------------------------------------------------------------------------------------------------------------------------------------------------------------------

g1 <- ggplot(charges_graph_temp, aes(x = Date, y = Charges)) + 
  geom_bar(stat = "identity") + 
  theme_stata(base_size = 11) + 
  scale_y_continuous(
    name = "Charges", 
    labels = scales::comma,
    breaks = pretty_breaks(4)
    ) +
  ggtitle("Total Charges by Month")

g2 <- ggplot(
  charges_graph_temp, 
  aes(
    x = Date, 
    y = Charges, 
    fill = MPS
    )
  ) + 
  geom_bar(
    position = "fill", 
    stat = "identity"
    ) + 
  theme_stata(base_size = 11) + 
  scale_y_continuous(
    name = "Proportion of Monthly Charge",
    breaks = c(0, 0.25, 0.5, 0.75, 1)
  ) +
  theme(legend.title = element_blank()) +
  ggtitle("Breakdown of Charges by MPS")

gg <- gridExtra::arrangeGrob(g1, g2, nrow = 2, ncol = 1)

plot(gg)

```

\newpage

## MPS Performance Flags

`r TRADING.PARTY` has had `r nrow(tracking_performance_temp)` performance flag(s).

```{r echo = FALSE, results = "asis"}

if (nrow(tracking_performance_temp) > 0) {

kable(tracking_performance_temp, 
      format = "latex", 
      caption = "Flags for below peer performance", 
      col.names = c("Date", "MPS", "Action", "Rationale"), 
      booktabs = TRUE, 
      linesep = "",
      format.args = list(big.mark = ",")
      ) %>%
  kable_styling(
    latex_options = c(
      "repeat_header", 
      "hold_position", 
      "striped", 
      position = "center", 
      full_width = FALSE)
    ) %>%
  column_spec(4, width = "8.5cm") %>%
  row_spec(0, bold = TRUE)

}

```

Where an Action is recorded as "Watch", the performance issue will be added to MOSL's watch-list of performance issues. Any performance issue(s) on the watch-list could be closely monitored over a number of months. If the issue is not resolved then it could be escalated to an IPRP. `r TRADING.PARTY` currently has `r nrow(tracking_watch_temp)` performance issues on Watch. 

```{r echo = FALSE, results = "asis"}

if (nrow(tracking_watch_temp) > 0) {

kable(tracking_watch_temp, 
      format = "latex", 
      caption = "Performance issues currently on Watch", 
      col.names = c("Trading Party", "MPS"), 
      booktabs = TRUE,
      longtable = TRUE,
      linesep = "",
      format.args = list(big.mark = ",")
      ) %>%
  kable_styling(
    latex_options = c(
      "repeat_header", 
      "hold_position", 
      "striped", 
      position = "center", 
      full_width = FALSE)
    ) %>%
  row_spec(0, bold = TRUE)

}

```

Below is a summary (where applicable) of the commentary that MOSL has received, via the Portfolio Manager, regarding any watch-list items or flagged performance issues:

```{r echo = FALSE, results = "asis"}

if (nrow(tracking_pfm_mpsperf_temp) > 0) {

kable(tracking_pfm_mpsperf_temp, 
      format = "latex", 
      caption = "PFM Commentary", 
      col.names = c("Date", "MPS", "Commentary"), 
      booktabs = TRUE,
      longtable = TRUE,
      linesep = "",
      format.args = list(big.mark = ",")
      ) %>%
  kable_styling(
    latex_options = c(
      "repeat_header", 
      "hold_position", 
      "striped", 
      position = "center", 
      full_width = FALSE)
    ) %>%
  column_spec(3, width = "10cm") %>%
  row_spec(0, bold = TRUE)

}

```

## Trading Party Performance Graphs (MPS)

MOSL uses performance graphs as a monitoring tool to identify issues. The performance graphs for `r TRADING.PARTY` are shown below.

```{r message=FALSE, echo=FALSE, error=FALSE, warning=FALSE}

labels <- c("TP On-Time Tasks (RHS)", "Market Mean (RHS)", "Market Median (RHS)", "TP Task Share (RHS)")

plist = lapply(split(mps_data_melt_temp, mps_data_melt_temp$MPS), function(z) {
  
  data <- z

  plot <- ggplot(data) + 
    geom_bar(
      aes(
        x = data$Date, 
        y = data$TaskVolume, 
        fill="Task Volume (LHS)"
        ),
      stat = "identity", 
      position = "dodge", 
      inherit.aes = FALSE
      ) +
    geom_line(
      aes(
        x = data$Date, 
        y = data$value * max(data$TaskVolume), 
        colour = data$variable,
        linetype = data$variable, 
        size = data$variable
        )
      ) + 
    scale_y_continuous(
      breaks = pretty_breaks(4),
      sec.axis = 
        sec_axis(~. / max(data$TaskVolume), name = "Proportion")
      ) +
    scale_fill_manual(NULL, values = "azure3", na.value = "red") +
    scale_size_manual(values = c(1, 0.5, 0.5, 0.5), na.value = "1", labels = labels) +
    scale_linetype_manual(values = c(1, 2, 1, 3), na.value = "1", labels = labels) +
    scale_colour_manual(values = c("darkorange", "azure4", "dodgerblue4", "grey3"), 
                        na.value = "red", labels = labels) +
    ylab("Volume of tasks") + xlab("Date") +
    theme(legend.title = element_blank(), legend.position = "right") +
    ggtitle(paste(data$Trading.Party.ID, " (", data$MPS, ")", sep=""))
  
  }
)

gridExtra::marrangeGrob(plist,top=NULL,nrow=1,ncol=1)


```

\newpage

# MPS Performance Rectification

`r if (nrow(iprp_status_temp) > 0) { "## IPRP Status Summary" }`

`r TRADING.PARTY` currently has `r nrow(iprp_status_temp)` active IPRP(s).

```{r echo = FALSE, results = "asis"}

if(nrow(iprp_status_temp) > 0){

  kable(
    iprp_status_temp, 
    format = "latex", 
    caption = "Current status of IPRP(s)", 
    col.names = c(
      "Date", 
      "MPS", 
      "Batch", 
      "Actual Perf.", 
      "Planned Perf.", 
      "Status"), 
    longtable = FALSE, 
    booktabs = TRUE, 
    linesep = ""
    ) %>%
    kable_styling(
      latex_options = 
        c(
          "repeat_header",
          "hold_position",
          "striped",
          position= "center", 
          full_width = TRUE
          )
      ) %>%
    row_spec(0, bold = TRUE)
  
}

```

`r if(nrow(tracking_milestone_temp) > 0) { paste("Below is a table summarising details of the IPRP Milestone flags for ", TRADING.PARTY, ".", sep = "") }`

```{r echo = FALSE, results = "asis"}

if(nrow(tracking_milestone_temp) > 0) {

  kable(
    tracking_milestone_temp, 
    format = "latex", 
    caption = "IPRPs flagged as below milestone",
    col.names = c(
      "Date", 
      "MPS", 
      "Batch", 
      "Action", 
      "Rationale"), 
    longtable = TRUE, 
    booktabs = TRUE, 
    linesep = ""
    ) %>%
    kable_styling(
      latex_options = 
        c(
          "repeat_header",
          "hold_position", 
          "striped", 
          position = "center", 
          full_width = FALSE
          )
      ) %>%
    column_spec(5, width = "7cm") %>%
    row_spec(0, bold = TRUE)
  
}

```

`r if (nrow(tracking_pfm_mile_temp) > 0) { paste("Below is a summary of the commentary that MOSL has received via the Portfolio Manager regarding the milestone performance flags:") }` 

```{r echo = FALSE, results = "asis"}

if (nrow(tracking_pfm_mile_temp) > 0) {

kable(tracking_pfm_mile_temp, 
      format = "latex", 
      caption = "PFM Commentary", 
      col.names = c("Date", "MPS", "Commentary"), 
      booktabs = TRUE,
      longtable = TRUE,
      linesep = "",
      format.args = list(big.mark = ",")
      ) %>%
  kable_styling(
    latex_options = c(
      "repeat_header", 
      "hold_position", 
      "striped", 
      position = "center", 
      full_width = FALSE)
    ) %>%
  column_spec(3, width = "10cm") %>%
  row_spec(0, bold = TRUE)

}

```

\newpage

`r if (nrow(iprp_status_temp) > 0) { "## IPRP Graphs" }`

`r if (nrow(iprp_status_temp) > 0) { paste("The graphs below depict the performance of each IPRP against its planned milestones.") }`

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE}

if (nrow(iprp_status_temp) > 0) {

##producing the graphs as list then using marrangeGrob

iprp_labels <- c("Task Completion (RHS)", "Mean (RHS)", "Median (RHS)", "Task Share (RHS)", "Planned Perf (RHS)")

for (v in IPRP_list) {
  
  data <- IPRP_plans_melt_temp %>%
    filter(MPS == v)

  plot <- ggplot(data) + 
    geom_bar(
      aes(
        x = data$Date, 
        y = data$TaskVolume,
        fill = "Task Volume (LHS)"
        ), 
      stat = "identity",
      position = "dodge", 
      inherit.aes = FALSE
      ) +
    geom_line(
      aes(
        x = data$Date, 
        y = data$value * max(data$TaskVolume),
        colour = data$variable, 
        linetype = data$variable,
        size = data$variable
        )
      ) + 
    geom_point(
      aes(
        x = data$Date, 
        y = data$value * max(data$TaskVolume),
        shape = data$variable, 
        alpha = data$variable
        )
      ) +
    scale_y_continuous(
      breaks = pretty_breaks(4),
      sec.axis = 
        sec_axis(~. / max(data$TaskVolume), name = "Proportion")
      ) +
    scale_fill_manual(NULL, values = "azure3", na.value = "red") +
    scale_size_manual(values = c(1,0.5,0.5,0.5,1), na.value = "1", labels = iprp_labels) +
    scale_linetype_manual(values = c(1,2,1,3,1), na.value = "1", labels = iprp_labels) +
    scale_colour_manual(
      values = 
        c("darkorange", "azure4", "dodgerblue4","grey3","red"),
      na.value = "red", 
      labels = iprp_labels
      ) +
    scale_shape_manual(values = c(0,0,0,0,1), na.value = 0,labels = iprp_labels) +
    scale_alpha_manual(values = c(0,0,0,0,1), na.value = 0, labels = iprp_labels) +
    ylab("Volume of tasks") + xlab("Date") +
    theme(legend.title = element_blank(), legend.position = "right") +
    ggtitle(
      paste(
        "Batch ", 
        max(as.numeric(data$Batch), na.rm = TRUE), 
        ": ", 
        data$Trading.Party.ID, 
        "  (", 
        data$MPS,
        ")", 
        sep="")
      )
  
  print(plot)
  
  }

}

```

\newpage

# MPS Market Aggregates

```{r echo = FALSE, results = "asis"}

kable(mps_summary_mean_temp, 
      format = "latex", 
      caption = "Mean peer performance", 
      booktabs = TRUE, 
      linesep = "",
      digits = 1,
      format.args = list(decimal.mark = ".", big.mark = ",")) %>%
  kable_styling(
    latex_options = 
      c(
        "repeat_header", 
        "hold_position", 
        "striped", 
        position = "center", 
        full_width = TRUE, 
        "scale_down"
        )
    ) %>%
  row_spec(0, bold = TRUE)

```

```{r echo = FALSE, results = "asis"}

kable(mps_summary_median_temp, 
      format = "latex", 
      caption = "Median peer performance", 
      booktabs = TRUE, 
      linesep = "",
      digits = 1,
      format.args = list(decimal.mark = ".", big.mark = ",")) %>%
  kable_styling(
    latex_options = 
      c(
        "repeat_header", 
        "hold_position",
        "striped", 
        position = "center", 
        full_width = TRUE, 
        "scale_down"
        )
    ) %>%
  row_spec(0, bold = TRUE)

```

```{r echo = FALSE, results = "asis"}

kable(mps_summary_tasks_temp, 
      format = "latex", 
      caption = "Aggregate task volumes", 
      booktabs = TRUE, 
      linesep = "",
      format.args = list(big.mark = ",")) %>%
  kable_styling(
    latex_options = 
      c(
        "repeat_header", 
        "hold_position", 
        "striped", 
        position = "center",
        full_width = TRUE, 
        "scale_down"
        )
    ) %>%
  row_spec(0, bold = TRUE)

```

\newpage

`r if (nrow(ops_data_temp) > 0) { "# Trading Party OPS Performance" }`

`r if (nrow(ops_data_temp) > 0) { "## Trading Party Performance Graphs (OPS)" }`

`r if (nrow(ops_data_temp) > 0) { paste("MOSL uses performance graphs as a monitoring tool to identify issues. The performance graphs for ", TRADING.PARTY, " are shown below.", sep = "") }`

```{r message=FALSE, echo=FALSE, error=FALSE, warning=FALSE}

if (nrow(ops_data_temp) > 0) {

  labels <- c("TP On-Time Tasks (RHS)", "Market Mean (RHS)", "Market Median (RHS)", "TP Task Share (RHS)")
  
  oplist = lapply(split(ops_data_melt_temp, ops_data_melt_temp$key), function(v) {
    
    data <- v
  
    plot <- ggplot(data) + 
      geom_bar(
        aes(
          x = data$Date, 
          y = data$TaskVolume, 
          fill="Task Volume (LHS)"
          ),
        stat = "identity", 
        position = "dodge", 
        inherit.aes = FALSE
        ) +
      geom_line(
        aes(
          x = data$Date, 
          y = data$value * max(data$TaskVolume), 
          colour = data$variable,
          linetype = data$variable, 
          size = data$variable
          )
        ) + 
      scale_y_continuous(
        breaks = pretty_breaks(4),
        sec.axis = 
          sec_axis(~. / max(data$TaskVolume), name = "Proportion")
        ) +
      scale_fill_manual(NULL, values = "azure3", na.value = "red") +
      scale_size_manual(values = c(1, 0.5, 0.5, 0.5), na.value = "1", labels = labels) +
      scale_linetype_manual(values = c(1, 2, 1, 3), na.value = "1", labels = labels) +
      scale_colour_manual(
        values = c("darkorange", "azure4", "dodgerblue4", "grey3"),
        na.value = "red", labels = labels) +
      ylab("Volume of tasks") + xlab("Date") +
      theme(legend.title = element_blank(), legend.position = "right") +
      ggtitle(paste(data$Trading.Party.ID, " (", data$OPS, ")", sep=""))
    
    }
  )
  
  gridExtra::marrangeGrob(oplist,top=NULL,nrow=1,ncol=1)

}

```

\newpage

`r if(nrow(ops_data_temp) > 0) { "# OPS Market Aggregates" }`

```{r echo = FALSE, results = "asis"}

if (nrow(ops_data_temp) > 0) {
  
  kable(ops_summary_mean_temp, 
        format = "latex", 
        caption = "Mean peer performance", 
        booktabs = TRUE, 
        linesep = "",
        digits = 1,
        format.args = list(decimal.mark = ".", big.mark = ",")) %>%
    kable_styling(
      latex_options = 
        c(
          "repeat_header", 
          "hold_position", 
          "striped", 
          position = "center", 
          full_width = TRUE, 
          "scale_down"
          )
      ) %>%
    row_spec(0, bold = TRUE)

}

```

```{r echo = FALSE, results = "asis"}

if (nrow(ops_data_temp) > 0) {
  
  kable(ops_summary_median_temp, 
        format = "latex", 
        caption = "Median peer performance", 
        booktabs = TRUE, 
        linesep = "",
        digits = 1,
        format.args = list(decimal.mark = ".", big.mark = ",")) %>%
    kable_styling(
      latex_options = 
        c(
          "repeat_header", 
          "hold_position",
          "striped", 
          position = "center", 
          full_width = TRUE, 
          "scale_down"
          )
      ) %>%
    row_spec(0, bold = TRUE)

}

```

```{r echo = FALSE, results = "asis"}

if (nrow(ops_data_temp) > 0) {

  kable(ops_summary_tasks_temp, 
        format = "latex", 
        caption = "Aggregate task volumes", 
        booktabs = TRUE, 
        linesep = "",
        format.args = list(big.mark = ",")) %>%
    kable_styling(
      latex_options = 
        c(
          "repeat_header", 
          "hold_position", 
          "striped", 
          position = "center",
          full_width = TRUE, 
          "scale_down"
          )
      ) %>%
    row_spec(0, bold = TRUE)

}

```

# Appendix

## Performance Criteria

A Trading Party's MPS performance will be flagged when the ratio of on-time task completion to total tasks completed for that MPS falls below the peer mean and peer median level for three consecutive months. "Peer mean" and "peer median" refer, respectively, to the mean and median of all on-time task ratios for every Trading Party in the market. The following MPS are currently subject to this criteria: `r paste(mps_list_pr, sep = ", ")`.

When evaluating these performance flags, MOSL takes into account other factors, including: performance relative to comparable peers; number of tasks relative to size; and other important Trading Party activites, such as data improvement activity and significant operational changes.

Persistently poor performance could lead to the issue being escalated to MOSL's Performance Resolution process through an Initial Performance Rectification Plan (IPRP). Failure to improve over time at this stage could lead to the issue being further escalated to a Performance Rectification Plan (PRP) overseen by MPC and/or Panel.