---
title: 'Portfolio Manager Report: `r paste0(TRADING.PARTY.NAME, " (",TRADING.PARTY,")")`'
date: "`r format(Sys.Date(), '%B %Y')`"
fontsize: 12pt
output:
  pdf_document:
    fig_height: 3.2
    fig_width: 8
    number_section: yes
    toc: yes
    fig_caption: true
header-includes:
- \usepackage{titling}
- \pretitle{\begin{center}\LARGE\includegraphics[width=24cm]{mosl_title.png}\\[\bigskipamount]}
- \posttitle{\end{center}}
- \usepackage{xcolor}
- \usepackage{color}
- \usepackage{fancyhdr}
- \usepackage{graphicx}
- \usepackage{eurosym}
- \usepackage{longtable}
- \usepackage{booktabs}
- \usepackage{makecell}
- \usepackage{pdflscape}
- \usepackage{multirow}
- \pagestyle{fancy}
- \fancyhf{}
- \lfoot{MOSL Performance Report}
- \rhead{\includegraphics[width=6cm]{mosl_header.png}}
- \rfoot{Page \thepage}
classoption: table
---

# Market Performance Standards

## Performance Charges

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, fig.width = 12, fig.height = 5}

mps_data_clean_temp %>%
  dplyr::select(
    Trading.Party.ID, Date, MPS, Charges
    ) %>%
  ggplot2::ggplot(
    ggplot2::aes(x = Date, y = Charges, fill = MPS)
    ) + 
  ggplot2::geom_bar(stat = "identity") + 
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    text = ggplot2::element_text(size = 15)
    ) +
  ggplot2::scale_y_continuous(
    labels = scales::comma,
    breaks = scales::pretty_breaks(4)
    ) +
  ggplot2::labs(
    title = "Performance Charges",
    subtitle = "Breakdown by month and standard",
    caption = "Source: MOSL"
    ) +
  ggplot2::ylab("Charges (£)") + ggplot2::xlab("")

```

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE}

# Creating table of charges by MPS ---------------- 

mps_data_clean_temp %>%
  dplyr::filter(
    Date >= max(mps_data_clean_temp$Date) %m-% months(11)
    ) %>%
  dplyr::select(Date, MPS, Charges) %>%
  dplyr::mutate(Date = format(Date, "%Y-%m")) %>% 
  tidyr::spread(MPS, Charges) %>%
  dplyr::mutate(
    Total = rowSums(dplyr::select(., -Date), na.rm = TRUE)
    ) %>%
  kableExtra::kable (
    format = "latex", 
    caption = "Breakdown of Charges by MPS", 
    linesep = "",
    format.args = list(big.mark = ","),
    booktabs = TRUE,
    align = "c"
    ) %>%
  kableExtra::kable_styling(
    font_size = 10,
    latex_options = c(
      "repeat_header",
      "hold_position",
      "striped",
      position = "center", 
      full_width = FALSE,
      "scale_down"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)


```

## On-Time Task Completion

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, fig.width = 12, fig.height = 5}


rect_df <- data.frame(
  xmin = rep(min(mps_data_clean_temp$Date), 4), 
  xmax = rep(max(mps_data_clean_temp$Date), 4), 
  ymin = c(0.9, 0.8, 0.7, 0), 
  ymax = c(1, 0.9, 0.8, 0.7), 
  cat = 
    factor(
      c("Very good", "Good", "Poor", "Very poor"), 
      levels = c("Very good", "Good", "Poor", "Very poor")
      )
  )

mps_data_clean_temp %>%
  dplyr::left_join(
    dplyr::filter(
      dplyr::select(
        mps_sum_TradingParties, 
        Trading.Party.ID, Date, 
        Agg_Perf_roll
        ), 
      Trading.Party.ID == TRADING.PARTY
      ),
    by = c("Date")
    ) %>%
  dplyr::mutate(
    MPS = factor(
        MPS,
        levels = c(
          "MPS 1", "MPS 2", "MPS 3", "MPS 4", "MPS 5", "MPS 6", "MPS 7",
          "MPS 8", "MPS 9", "MPS 10", "MPS 12", "MPS 13", "MPS 14",
          "MPS 15", "MPS 16", "MPS 17", "MPS 18", "MPS 19"
          )
        )
    ) %>%
  droplevels() %>%
  ggplot2::ggplot() + 
  ggplot2::geom_line(
    ggplot2::aes(
      x = Date, 
      y = TaskCompletion, 
      colour = MPS
      )
    ) +
  ggplot2::geom_line(
    ggplot2::aes(
      x = Date, 
      y = Agg_Perf_roll,
      colour = "Agg. Performance"
      ),
    linetype = "dashed",
    size = 1
    ) +
  ggplot2::geom_rect(
      data = rect_df, 
      ggplot2::aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = cat), 
      alpha = 0.1
      ) +
    ggplot2::scale_fill_manual(
      values = c("green4", "greenyellow", "orange1", "orangered1")
      ) +
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    text = ggplot2::element_text(size = 15)
    ) +
  ggplot2::scale_y_continuous(
    breaks = scales::pretty_breaks(4)
    ) +
  ggplot2::labs(
    title = paste0("MPS On-Time Task Completion: ", SHORT.NAME),
    subtitle = "Breakdown by month and standard",
    caption = "Source: MOSL\nNote: Aggregate performance corresponds to the 6-month average of aggregate MPS performance"
    ) +
  ggplot2::ylab("") + ggplot2::xlab("")

```

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis"}

mps_data_clean_temp %>% 
  dplyr::filter(
    Date >= max(mps_data_clean_temp$Date) %m-% months(12)
    ) %>%
  dplyr::mutate(
    TaskCompletion = format(TaskCompletion, digits = 2),
    Date = format(Date, "%Y-%m")
    ) %>%
  dplyr::select(
    Date, MPS, TaskCompletion
    ) %>%
  tidyr::spread(key = MPS, value = TaskCompletion) %>%
  kableExtra::kable(
    format = "latex", 
    caption = "MPS Performance by Month",
    linesep = "",
    format.args = list(big.mark = ","),
    booktabs = TRUE,
    align = "c"
    ) %>%
  kableExtra::kable_styling(
    font_size = 10,
    latex_options = c(
      "repeat_header",
      "hold_position",
      "striped",
      position = "center", 
      full_width = FALSE,
      "scale_down"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)

```

`r SHORT.NAME`'s 6-month average aggregate MPS performance is `r format(mps_sum_TradingParties_temp$Agg_Perf_roll, digits = 2)`, which currently ranks as:

* `r scales::ordinal(mps_sum_TradingParties_temp$rank_all)` out of `r mps_sum_TradingParties_temp$n_all` for all Trading Parties
* `r scales::ordinal(mps_sum_TradingParties_temp$rank_type)` out of `r paste0(mps_sum_TradingParties_temp$n_type, " ", mps_sum_TradingParties_temp$tp_type)`s
* `r scales::ordinal(mps_sum_TradingParties_temp$rank_subtype)` out of `r mps_sum_TradingParties_temp$n_subtype` trading parties with licence type `r mps_sum_TradingParties_temp$sub_type`

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, fig.width = 12, fig.height = 6}

mps_sum_TradingParties %>%
  dplyr::filter(
    sub_type == as.character(mps_sum_TradingParties_temp$sub_type),
    Date == data.period
    ) %>%
  ggplot2::ggplot() +
  ggplot2::geom_bar(
    ggplot2::aes(
      x = reorder(ShortName, Agg_Perf_roll), 
      y = Agg_Perf_roll,
      fill = dplyr::if_else(Trading.Party.ID == TRADING.PARTY, "highlight", "normal")
      ), 
    stat = "identity",
    show.legend = FALSE) +
  ggplot2::scale_fill_manual(values = c("grey4", "azure4")) +
  ggplot2::coord_flip() +
  ggplot2::theme(
    text = ggplot2::element_text(size = 15)
    ) +
  ggplot2::labs(
    title = "Ranking of Aggregate MPS Performance",
    subtitle = 
      paste0(
        "6-month mean of aggregate MPS performance by Trading Party (", 
        mps_sum_TradingParties$sub_type, ")"
        ),
    caption = "Source: MOSL"
    ) +
  ggplot2::ylab("") + ggplot2::xlab("")

```

## Performance Issues

At the beginning of the period (`r format(data.period, "%Y-%m")`), `r SHORT.NAME` had `r nrow(perf_status_mps_temp)` standards being monitored by MOSL. A summary of each standard is shown in the table below: 

``` {r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis"}

perf_status_mps_temp %>%
  dplyr::select(
    MPS, SecondaryCategory, Consistency, PerfRating, Status, Action
    ) %>%
  kableExtra::kable(
    format = "latex", 
    caption = "Current MPS Categorisation and MOSL Actions",
    linesep = "",
    booktabs = TRUE,
    col.names = c("MPS", "Category", "Consistency", "Performance Rating", "IPRP Status", "MOSL Action"),
    align = c("llcccc")
    ) %>%
  kableExtra::column_spec(4:6, width = "2.5cm") %>%
  kableExtra::kable_styling(
    latex_options = c(
      "repeat_header",
      "hold_position",
      "striped",
      position = "center", 
      full_width = FALSE,
      "scale_down"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)

```

<br>

## MPS Analysis

As part of its analysis of historical MPS performance, MOSL categorises performance over a 6-month period according to consistency and by comparing performance to the market mean performance over the same period. For example, mean performance over six-months at, or close to, the mean market level, in most months (i.e. 3 or more of the last 6 months) would be rated as “consistent, good”. 

See Appendix I for further information of how MOSL categorises MPS performance. 

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis"}

mps_list <- unique(as.character(perf_status_mps_temp$MPS))

res <- lapply(mps_list, function (MPS_CHUNK) {
  
  knitr::knit_child(
    "pfm_report_mps_template.Rmd", envir = environment(), quiet = TRUE
  )
  
})

cat(unlist(res), sep = "\n")

```

## MPS Market Aggregates

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis"}

mps_summary %>% 
  dplyr::select(
    Date, MPS, MPS_Mean
    ) %>% 
  dplyr::filter(
    Date >= data.period %m-% months(11)
    ) %>% 
  dplyr::mutate(Date = format(Date, "%Y-%m")) %>%
  tidyr::spread(MPS, MPS_Mean) %>%
  kableExtra::kable(
    format = "latex", 
    caption = "Mean peer performance", 
    linesep = "",
    digits = 1,
    format.args = list(decimal.mark = ".", big.mark = ","),
    booktabs = TRUE,
    align = "c"
    ) %>%
  kableExtra::kable_styling(
    latex_options = c(
      "repeat_header",
      "hold_position",
      "striped",
      "scale_down"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)

```

<br>

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis"}

mps_summary %>% 
  dplyr::select(
    Date, MPS, MPS_Median
    ) %>% 
  dplyr::filter(
    Date >= data.period %m-% months(11)
    ) %>% 
  dplyr::mutate(Date = format(Date, "%Y-%m")) %>%
  tidyr::spread(MPS, MPS_Median) %>%
  kableExtra::kable(
    format = "latex", 
    caption = "Median peer performance", 
    linesep = "",
    digits = 1,
    format.args = list(decimal.mark = ".", big.mark = ","),
    booktabs = TRUE,
    align = "c"
    ) %>%
  kableExtra::kable_styling(
    latex_options = c(
      "repeat_header",
      "hold_position",
      "striped",
      "scale_down"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)

```

<br>

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis"}

mps_summary %>% 
  dplyr::select(
    Date, MPS, TotalTaskVolume
    ) %>% 
  dplyr::filter(
    Date >= data.period %m-% months(11)
    ) %>% 
  dplyr::mutate(Date = format(Date, "%Y-%m")) %>%
  tidyr::spread(MPS, TotalTaskVolume) %>%
  kableExtra::kable(
    format = "latex", 
    caption = "Total Task Volume", 
    linesep = "",
    digits = 1,
    format.args = list(decimal.mark = ".", big.mark = ","),
    booktabs = TRUE,
    align = "c"
    ) %>%
  kableExtra::kable_styling(
    latex_options = c(
      "repeat_header",
      "hold_position",
      "striped",
      "scale_down"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)

```

\newpage

# Appendix

## Performance Criteria

A Trading Party's MPS performance will be flagged when the ratio of on-time task completion to total tasks completed for that MPS falls below the peer mean and peer median level for three consecutive months. "Peer mean" and "peer median" refer, respectively, to the mean and median of all on-time task ratios for every Trading Party in the market. The following MPS are currently subject to this criteria: MPS 1, MPS 2, MPS 3, MPS 4, MPS 7, MPS 12, MPS 16, MPS 17.

MPS performance will also be flagged when it is lower than the threshold percentage, set by MOSL. This threshold performance can change when MOSL feel appropriate. Currently, only MPS 18 is subject to a threshold (75%).

When evaluating these performance flags, MOSL takes into account other factors, including: performance relative to comparable peers; number of tasks relative to size; and other important Trading Party activities, such as data improvement activity and significant operational changes.

Persistently poor performance could lead to the issue being escalated to MOSL's Performance Resolution process through an Initial Performance Rectification Plan (IPRP). Failure to improve over time at this stage could lead to the issue being further escalated to a Performance Rectification Plan (PRP) overseen by MPC and / or Panel.
