---
title: 'Monthly Performance Report'
date: "`r format(as.Date(data.period), '%B %Y')`"
fontsize: 12pt
output:
  pdf_document:
    fig_height: 3.2
    fig_width: 8
    number_section: yes
    toc: yes
    fig_caption: true
header-includes:
- \usepackage{titling}
- \pretitle{\begin{center}\LARGE\includegraphics[width=24cm]{mosl_title.png}\\[\bigskipamount]}
- \posttitle{\end{center}}
- \usepackage{xcolor}
- \usepackage{color}
- \usepackage{fancyhdr}
- \usepackage{graphicx}
- \usepackage{eurosym}
- \usepackage{longtable}
- \usepackage{booktabs}
- \usepackage{makecell}
- \usepackage{pdflscape}
- \usepackage{multirow}
- \usepackage{float}
- \pagestyle{fancy}
- \fancyhf{}
- \lfoot{MOSL Performance Report}
- \rhead{\includegraphics[width=6cm]{mosl_header.png}}
- \rfoot{Page \thepage}
classoption: table
---

# Market Performance Standards

## Performance Charges

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, fig.width = 12, fig.height = 5}

mps_data_clean %>%
  dplyr::filter(
    Period <= data.period
    ) %>%
  dplyr::select(
    Period, Charges, Group
    ) %>%
  dplyr::group_by(Period, Group) %>%
  dplyr::summarise(
    Charges = sum(Charges)
    ) %>%
  ggplot2::ggplot(
    ggplot2::aes(x = Period, y = Charges, fill = Group)
    ) + 
  ggplot2::geom_bar(stat = "identity") + 
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    text = ggplot2::element_text(size = 15)
    ) +
  ggplot2::scale_y_continuous(
    labels = scales::dollar_format(prefix = "£"),
    breaks = scales::pretty_breaks(4)
    ) +
  ggplot2::theme_bw() +
  ggplot2::scale_fill_manual(values = c("#425563", "#05C3DE", "#005F83", "#00A499", "#FFAA4D", "#F9E547", "#8866BC")) +
  ggplot2::labs(
    title = "Performance Charges",
    subtitle = "Breakdown by month and standard grouping",
    caption = "Source: MOSL"
    ) +
  ggplot2::ylab("") + ggplot2::xlab("")

```

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE}

# Creating table of charges by MPS ---------------- 

mps_data_clean %>%
  dplyr::filter(
      Period >= data.period %m-% months(11),
      Charges > 0
    ) %>%
  base::droplevels() %>%
  dplyr::select(Period, Standard, Charges) %>%
  dplyr::mutate(
    Period = format(Period, "%Y-%m"),
    Charges = tidyr::replace_na(Charges, 0)
    ) %>% 
  tidyr::drop_na(Charges) %>%
  base::droplevels() %>%
  dplyr::group_by(Period, Standard) %>%
  dplyr::summarise(
    Charges = sum(Charges, na.rm = TRUE)
    ) %>%
  dplyr::ungroup() %>%
  tidyr::spread(Standard, Charges) %>%
  dplyr::mutate(
    Total = rowSums(dplyr::select(., -Period), na.rm = TRUE)
  ) %>%
  dplyr::mutate_if(~ any(is.na(.)), ~ ifelse(is.na(.), 0, .)) %>%
  dplyr::mutate_if(is.numeric, scales::dollar_format(prefix = "£")) %>%
  tidyr::gather("Standard", "Charges", -Period) %>%
  tidyr::spread(Period, Charges) %>%
  kableExtra::kable(
    format = "latex", 
    caption = "Breakdown of Charges by Standard", 
    linesep = "",
    format.args = list(big.mark = ","),
    booktabs = TRUE,
    align = "c"
    ) %>%
  kableExtra::kable_styling(
    font_size = 10,
    latex_options = c(
      "repeat_header",
      "hold_position",
      "striped",
      position = "center", 
      full_width = FALSE,
      "scale_down"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)

```

## Performance Overview

As of `r format(data.period, "%B-%Y")`, MOSL were monitoring Trading Party performance against `r nrow(perf_status_mps)` standards. Performance for these standards is measured according to:

* `r paste(unique(perf_status_ops_temp$PerformanceMeasure), collapse = "and")`

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, fig.width = 12, fig.height = 5}

agg_perf <- mps_data_clean %>%
  dplyr::group_by(Period) %>%
  dplyr::summarise(
    Perf = sum(OnTimeTasks, na.rm = TRUE) / sum(TaskVolume, na.rm = TRUE)
    ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    Agg_Perf = zoo::rollapply(Perf, 6, mean, align = "right", fill = NA)
    ) %>%
  dplyr::rename(GroupPerf = Agg_Perf) %>%
  dplyr::mutate(Group = "Aggregate Performance")

mps_data_clean %>%
  dplyr::group_by(Period, Group) %>%
  dplyr::summarise(
    Perf = sum(OnTimeTasks) / sum(TaskVolume),
    ) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(Group) %>%
  dplyr::mutate(
    GroupPerf = zoo::rollapply(Perf, 6, mean, align = "right", fill = NA)
    ) %>%
  dplyr::ungroup() %>%
  base::rbind(., agg_perf) %>%
  droplevels() %>%
  tidyr::drop_na() %>%
  ggplot2::ggplot() + 
  ggplot2::geom_line(
    ggplot2::aes(
      x = Period, 
      y = GroupPerf, 
      colour = Group,
      linetype = Group
      )
    ) +
  ggplot2::geom_point(
    ggplot2::aes(
      x = Period, 
      y = GroupPerf,
      colour = Group,
      fill = Group,
      shape = Group
      )
    ) +
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    text = ggplot2::element_text(size = 15)
    ) +
  ggplot2::scale_y_continuous(
    labels = scales::percent_format(accuracy = 1),
    breaks = scales::pretty_breaks(4)
    ) +
  ggplot2::theme_bw() + 
  ggplot2::scale_colour_manual(
    values = c("#425563", "#05C3DE", "#005F83", "#00A499", "#FFAA4D", "#F9E547", "#8866BC")
    ) +
  ggplot2::scale_fill_manual(
    values = c("#425563", "#05C3DE", "#005F83", "#00A499", "#FFAA4D", "#F9E547", "#8866BC")
    ) +
  ggplot2::labs(
    title = paste0("MPS On-Time Task Completion"),
    subtitle = "Breakdown by month and standard",
    caption = "Source: MOSL\nNote: Aggregate performance corresponds to the 6-month average of aggregate MPS performance"
    ) +
  ggplot2::ylab("") + ggplot2::xlab("")

```


```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis"}

mps_data_clean %>% 
  dplyr::filter(
    Period >= max(mps_data_clean$Period) %m-% months(11)
    ) %>%
  dplyr::group_by(Period, Standard) %>%
  dplyr::summarise(
    Performance = sum(OnTimeTasks, na.rm = TRUE) / sum(TaskVolume, na.rm = TRUE)
    ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    Performance = scales::percent(Performance, accuracy = 1),
    Period = format(Period, "%Y-%m")
    ) %>%
  tidyr::spread(Period, Performance) %>%
  kableExtra::kable(
    format = "latex", 
    caption = "MPS Performance by Month",
    linesep = "",
    format.args = list(big.mark = ","),
    booktabs = TRUE,
    align = "c"
    ) %>%
  kableExtra::kable_styling(
    font_size = 10,
    latex_options = c(
      "repeat_header",
      "hold_position",
      "striped",
      position = "center", 
      full_width = FALSE,
      "scale_down"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)

```


## Performance Monitoring and Rectification

### Status Summary

### IPRP count & matrix

### overview of progress?

### Watch-list and areas of concern

## Detailed IPRP Analysis

## Market Aggregates

# MPOP Reporting

















