### `r paste0(OPS_CHUNK, ": ", Standards_details$Context[Standards_details$Standard == OPS_CHUNK])`

> `r Standards_details$Details[Standards_details$Standard == OPS_CHUNK]`

```{r message = FALSE, echo = FALSE, error = TRUE, warning = FALSE}

OPS_TASKS_COMP <- perf_status_ops_temp %>%
  dplyr::filter(Standard == OPS_CHUNK, PerformanceMeasure == "Completed") %>%
  dplyr::pull(TaskVolume)

OPS_PERF_COMP <- perf_status_ops_temp %>%
  dplyr::filter(Standard == OPS_CHUNK, PerformanceMeasure == "Completed") %>%
  dplyr::pull(Performance)
  
OPS_TASKS_OUTS <- perf_status_ops_temp %>%
  dplyr::filter(Standard == OPS_CHUNK, PerformanceMeasure == "Outstanding") %>%
  dplyr::pull(TaskVolume)

OPS_PERF_OUTS <- perf_status_ops_temp %>%
  dplyr::filter(Standard == OPS_CHUNK, PerformanceMeasure == "Outstanding") %>%
  dplyr::pull(Performance)

OPS_SUMPERF3M_COMP <- perf_status_ops_temp %>%
  dplyr::filter(Standard == OPS_CHUNK, PerformanceMeasure == "Completed") %>%
  dplyr::pull(SumPerf3m)
  
OPS_SUMPERF3M_OUTS <- perf_status_ops_temp %>%
  dplyr::filter(Standard == OPS_CHUNK, PerformanceMeasure == "Outstanding") %>%
  dplyr::pull(SumPerf3m)
  
```

For `r format(data.period, "%B-%Y")`, `r SHORT.NAME` had:

* `r scales::comma(OPS_TASKS_COMP)` completed tasks for `r OPS_CHUNK` `r dplyr::if_else(!is.na(OPS_PERF_COMP), paste0("with on-time task completion of ", scales::percent(OPS_PERF_COMP)), "")`
* `r scales::comma(OPS_TASKS_OUTS)` outstanding tasks for `r OPS_CHUNK` `r dplyr::if_else(!is.na(OPS_PERF_OUTS), paste0("with on-time task completion of ", scales::percent(OPS_PERF_OUTS)), "")`

Below is a graph showing `r SHORT.NAME`'s historical performance for `r OPS_CHUNK`. MOSL action points and IPRP milestones are shown, if applicable. 

```{r message = FALSE, echo = FALSE, error = TRUE, warning = FALSE, fig.width = 12, fig.height = 5}

on_plan <- any(perf_status_ops_temp$IPRP[perf_status_ops_temp$Standard == OPS_CHUNK])

graph <- perf_status_ops %>%
  dplyr::filter(TaskVolume > 0) %>%
  MOSLR::plot_perf_graph(
    df = ., 
    load.data = FALSE,
    standard = OPS_CHUNK,
    trading.party = TRADING.PARTY,
    period.start = data.period %m-% months(11),
    period.end = data.period, 
    action.points = TRUE,
    include.iprp = on_plan,
    graph.title = OPS_CHUNK,
    sub.title = Standards_details$Context[Standards_details$Standard == OPS_CHUNK],
    ) +
  ggplot2::theme(text = ggplot2::element_text(size = 15)) +
  ggplot2::facet_wrap(~PerformanceMeasure)

tryCatch(
  expr = {
    plot(graph)
    },
  error = function(e){
    print(e)
  }
  )

```

Over the last 12 months, for `r OPS_CHUNK` there have been:

* `r OPS_SUMPERF3M_COMP` performance flag(s) for completed tasks
* `r OPS_SUMPERF3M_OUTS` performance flag(s) for outstanding tasks

`r if (on_plan) { paste0(OPS_CHUNK, " is currently on an IPRP. See below for further details.") }`

```{r message = FALSE, echo = FALSE, error = TRUE, warning = FALSE} 

RATIONALE_CHUNK <- perf_status_ops %>% 
  dplyr::filter(
    Period >= data.period %m-% months(6),
    Trading.Party.ID == TRADING.PARTY, 
    Standard == OPS_CHUNK, 
    Action != "") %>%
  nrow() > 0

PFM_COMM_CHUNK <- perf_status_ops %>% 
  dplyr::filter(
    Period >= data.period %m-% months(6),
    Trading.Party.ID == TRADING.PARTY, 
    Standard == OPS_CHUNK, 
    !is.na(PFM_Commentary), 
    PFM_Commentary != "") %>%
  nrow() > 0

```

<br> 

`r if (RATIONALE_CHUNK) { paste0("The table below shows the rationale for MOSL actions regarding ",  paste0(OPS_CHUNK), ".") }`

``` {r message = FALSE, echo = FALSE, error = TRUE, warning = FALSE, results = "asis", eval = RATIONALE_CHUNK}

comment_date <- perf_status_ops_temp %>%
  dplyr::filter(Standard == OPS_CHUNK) %>%
  dplyr::mutate(
    check = any(OnWatch, IPRP, PerfFlag3m, UnderReview),
    date = dplyr::if_else(check, as.Date("2018-04-01"), data.period %m-% months(6))
    ) %>%
  dplyr::pull(date)

perf_status_ops %>%
  dplyr::filter(
    Period >= comment_date,
    Trading.Party.ID == TRADING.PARTY,
    Standard == OPS_CHUNK,
    Action != ""
    ) %>%
  dplyr::select(Period, PerformanceMeasure, Action, Rationale) %>%
  dplyr::mutate(Period = format(as.Date(Period), "%Y-%m")) %>%
  kableExtra::kable(
    format = "latex", 
    caption = paste0("Rationale for Recent MOSL Actions for ", OPS_CHUNK),
    linesep = "",
    #longtable = TRUE, 
    booktabs = TRUE,
    col.names = c("Period", "Performance Measure", "Action", "Rationale")
    ) %>%
  kableExtra::column_spec(4, width = "7cm") %>%
  kableExtra::kable_styling(
    font_size = 10,
    latex_options = c(
      "repeat_header",
      "HOLD_position",
      full_width = TRUE, "striped"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)

```

<br> 

`r if (PFM_COMM_CHUNK) { paste0("The table below shows MOSL commentary regarding ",  paste0(OPS_CHUNK), ".") }`

``` {r message = FALSE, echo = FALSE, error = TRUE, warning = FALSE, results = "asis", eval = PFM_COMM_CHUNK}

perf_status_ops %>%
  dplyr::filter(
    Period >= comment_date,
    Trading.Party.ID == TRADING.PARTY,
    Standard == OPS_CHUNK,
    !is.na(PFM_Commentary), 
    PFM_Commentary != ""
    ) %>%
  dplyr::select(
    Period, PerformanceMeasure, PFM_Commentary
    ) %>%
  dplyr::mutate(
    Period = format(as.Date(Period), "%Y-%m")
    ) %>%
  kableExtra::kable(
    format = "latex", 
    caption = paste0("MOSL Commentary for ", OPS_CHUNK),
    linesep = "",
    #longtable = TRUE, 
    booktabs = TRUE,
    col.names = c("Period", "Performance Measure", "Portfolio Manager Commentary")
    ) %>%
  kableExtra::column_spec(3, width = "10cm") %>%
  kableExtra::kable_styling(
    font_size = 10,
    latex_options = c(
      "repeat_header",
      "HOLD_position",
      "striped"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)

```

<br> 

`r if (on_plan) { paste0("A summary of ", SHORT.NAME, "'s performance against its IPRP is shown in the table below.") }`

``` {r message = FALSE, echo = FALSE, error = TRUE, warning = FALSE, results = "asis", eval = on_plan}

perf_status_ops %>%
  dplyr::filter(
    Trading.Party.ID == TRADING.PARTY,
    Standard == OPS_CHUNK,
    ) %>%
  dplyr::mutate_if(is.numeric, scales::percent_format(accuracy = 1)) %>%
  dplyr::select(
    Period, PerformanceMeasure, Performance, Planned_Perf, DeltaQuant, Status
    ) %>%
  tidyr::drop_na() %>%
  dplyr::mutate(Period = format(as.Date(Period), "%Y-%m")) %>%
  kableExtra::kable(
    format = "latex", 
    caption = "IPRP Performance Tracking",
    linesep = "",
    #longtable = TRUE, 
    booktabs = TRUE,
    col.names = c("Period", "Performance Measure", "Actual Performance", "Planned Performance", "Relative Difference", "IPRP Status"),
    align = rep("c", 5)
    ) %>%
  kableExtra::column_spec(2:6, width = "2.5cm") %>%
  kableExtra::kable_styling(
    font_size = 10,
    latex_options = c(
      "repeat_header",
      "HOLD_position",
      "striped"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)

```

<br> 

`r if (on_plan) { paste0("For this standard there have been:") }`

`r if (on_plan) { paste0("* ",  sum(perf_status_ops_temp$CumResubmit[perf_status_ops_temp$Standard == OPS_CHUNK]), " IPRP resubmission(s)") }`
`r if (on_plan) { paste0("* ",  sum(perf_status_ops_temp$UnderReview[perf_status_ops_temp$Standard == OPS_CHUNK]), " IPRP review(s)") }`
