
### `r paste0(MPS_CHUNK, ": ", Standards_details$Context[Standards_details$Standard == MPS_CHUNK])`

> `r Standards_details$Details[Standards_details$Standard == MPS_CHUNK]`

`r SHORT.NAME`'s performance against `r MPS_CHUNK` is rated as:

* `r paste0(perf_status_mps_temp$Consistency[perf_status_mps_temp$Standard == MPS_CHUNK], ", ", perf_status_mps_temp$PerfRating[perf_status_mps_temp$Standard == MPS_CHUNK])`

Below is a graph showing `r SHORT.NAME`'s historical performance against `r MPS_CHUNK`. MOSL action points and Rectification milestones are shown, if applicable. 

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, fig.width = 12, fig.height = 5}

on.rectification <- perf_status_mps_temp$Rectification[perf_status_mps_temp$Standard == MPS_CHUNK]

graph <- perf_status_mps %>%
  dplyr::filter(
    TaskVolume > 0
    ) %>%
  MOSLR::plot_perf_graph(
    df = ., 
    load.data = FALSE,
    standard = MPS_CHUNK,
    trading.party = TRADING.PARTY,
    period.start = data.period %m-% months(11),
    period.end = data.period, 
    action.points = TRUE,
    include.iprp = on.rectification,
    graph.title = MPS_CHUNK,
    sub.title = Standards_details$Context[Standards_details$Standard == MPS_CHUNK],
    ) +
  ggplot2::theme(
    text = ggplot2::element_text(size = 15)
  )

tryCatch(
  expr = {
    plot(graph)
    },
  error = function(e){
    print(e)
  }
  )

```

For `r MPS_CHUNK` there have been:

* `r perf_status_mps_temp$SumPerf3m[perf_status_mps_temp$Standard == MPS_CHUNK]` performance flag(s)
* `r perf_status_mps_temp$CumWatch[perf_status_mps_temp$Standard == MPS_CHUNK]` watch flag(s)

`r if (on.rectification) { paste0(MPS_CHUNK, " is currently on a Rectification plan. See below for further details.") } else { paste0(MPS_CHUNK, " is not on a Rectification plan.") }`

<br> 

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE} 

RATIONALE_CHUNK <- nrow(perf_status_mps %>% dplyr::filter(Trading.Party.ID == TRADING.PARTY, Standard == MPS_CHUNK, Action != "")) > 0

PFM_COMM_CHUNK <- nrow(perf_status_mps %>% dplyr::filter(Trading.Party.ID == TRADING.PARTY, Standard == MPS_CHUNK, !is.na(PFM_Commentary), PFM_Commentary != "")) > 0

```

`r if (RATIONALE_CHUNK) { paste0("The table below shows the rationale for MOSL actions regarding ",  paste0(MPS_CHUNK), ".") }`

``` {r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis", eval = RATIONALE_CHUNK}

perf_status_mps %>%
  dplyr::filter(
    Trading.Party.ID == TRADING.PARTY,
    Standard == MPS_CHUNK,
    Action != ""
    ) %>%
  dplyr::select(
    Period, Action, Rationale
    ) %>%
  dplyr::mutate(
    Period = format(Period, "%Y-%m")
    ) %>%
  kableExtra::kable(
    format = "latex", 
    caption = "Rationale for Recent MOSL Actions",
    linesep = "",
    longtable = TRUE, 
    booktabs = TRUE,
    col.names = c("Period", "Action", "Rationale")
    ) %>%
  kableExtra::column_spec(3, width = "10cm") %>%
  kableExtra::kable_styling(
    font_size = 10,
    latex_options = c(
      "repeat_header",
      "hold_position",
      #full_width = TRUE,
      "striped"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)

```

<br> 

`r if (PFM_COMM_CHUNK) { paste0("The table below shows the commentary MOSL has received from Portfolio Managers regarding ",  paste0(MPS_CHUNK), ".") }`

``` {r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis", eval = PFM_COMM_CHUNK}

perf_status_mps %>%
  dplyr::filter(
    Trading.Party.ID == TRADING.PARTY,
    Standard == MPS_CHUNK,
    !is.na(PFM_Commentary), 
    PFM_Commentary != ""
    ) %>%
  dplyr::select(
    Period, PFM_Commentary
    ) %>%
  dplyr::mutate(
    Period = format(Period, "%Y-%m")
    ) %>%
  kableExtra::kable(
    format = "latex", 
    caption = "Rationale for Recent MOSL Actions",
    linesep = "",
    longtable = TRUE, 
    booktabs = TRUE,
    col.names = c("Period", "Portfolio Manager Commentary")
    ) %>%
  kableExtra::column_spec(2, width = "12cm") %>%
  kableExtra::kable_styling(
    font_size = 10,
    latex_options = c(
      "repeat_header",
      "hold_position",
      "striped"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)

```

<br> 

`r if (on.rectification) { paste0("A summary of ", SHORT.NAME, "'s performance against its Rectification plan is shown in the table below.") }`

``` {r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis", eval = on.rectification}

table <- perf_status_mps %>%
  dplyr::filter(
    Trading.Party.ID == TRADING.PARTY,
    Standard == MPS_CHUNK,
    ) %>%
  dplyr::mutate_if(is.numeric, scales::percent_format(accuracy = 1)) %>%
  dplyr::select(
    Period, Performance, Planned_Perf, DeltaQuant, Status
    ) %>%
  tidyr::drop_na() %>%
  dplyr::mutate(Period = format(Period, "%Y-%m"))

if (nrow(table) > 0) {

  table %>%
    kableExtra::kable(
      format = "latex", 
      caption = "Rectification Performance Tracking",
      linesep = "",
      longtable = TRUE, 
      booktabs = TRUE,
      col.names = c(
        "Period", "Actual Performance", "Planned Performance", 
        "Relative Difference", "Rectification Status"
        ),
      align = rep("c", 5)
      ) %>%
    kableExtra::column_spec(1:5, width = "2.5cm") %>%
    kableExtra::kable_styling(
      font_size = 10,
      latex_options = c(
        "repeat_header",
        "hold_position",
        "striped"
        )
      ) %>%
    kableExtra::row_spec(0, bold = TRUE)

  }

```

<br> 

`r if (on.rectification) { paste0("For this plan there have been:") }`

`r if (on.rectification) { paste0("* ",  perf_status_mps_temp$CumResubmit[perf_status_mps_temp$Standard == MPS_CHUNK], " resubmission(s)") }`
`r if (on.rectification) { paste0("* ",  sum(perf_status_mps_temp$UnderReview[perf_status_mps_temp$Standard == MPS_CHUNK]), " review(s)") }`
