### `r paste0(MPS, ": ", MPS_details$Context[MPS_details == MPS, ])`

MPS description: `r paste0(MPS_details$Details[MPS_details == MPS, ])`

`r SHORT.NAME`'s on-time task performance for `r MPS`  is rated as `r paste0("consistent, very good")`.

Below is a graph showing `r SHORT.NAME`'s historical on-time task completion performance for `r MPS`. 

```{r}

active.iprp <- MPS %in% IPRP_list

mps_data_melt %>%
  dplyr::filter(
    MPS == MPS
    ) %>%
  MOSLR::plot_mps_perf_graph(data = ., IPRP = active.iprp)

```

```{r}

rationale_temp_table <- tracking %>%
  filter(MPS == MPS) %>%
  select(Date, Action, Rationale)

pfm_com_temp_table <- tracking %>%
  filter(MPS == MPS) %>%
  select(Date, PFM_Commentary)

```


`r SHORT.NAME` have had no IPRPs issued for this standard over the last 12-months. The table below shows recent MOSL actions and rationale regarding this standard.

`r SHORT.NAME` have had no performance issues flagged for this standard over the last 12-months. 

```{r echo = FALSE, eval = nrow(rat_temp_table) > 0}

kable(
  rat_temp_table
)

```

The table below shows the PFM commentary received by MOSL.
There is no PFM commentary associated with this standard.

```{r echo = FALSE, eval = nrow(pfm_temp_table) > 0}

kable(
  pfm_temp_table
)

```
