# Operational Performance Standards

## Performance Charges

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, fig.width = 12, fig.height = 5}

tryCatch(
  expr = {
  ops_data_clean_temp %>%
    dplyr::filter(
      Charges > 0
      ) %>%
    tidyr::drop_na(Charges) %>%
    base::droplevels() %>%
    ggplot2::ggplot(
      ggplot2::aes(x = Period, y = Charges, fill = Group)
      ) + 
    ggplot2::geom_bar(stat = "identity") + 
    ggplot2::theme(
      text = ggplot2::element_text(size = 15)
      ) +
    ggplot2::scale_y_continuous(
      labels = scales::dollar_format(prefix = "£"),
      breaks = scales::pretty_breaks(4)
      ) +
    ggplot2::theme_bw() + 
    ggplot2::scale_fill_manual(values = c("#425563", "#05C3DE", "#005F83", "#00A499", "#FFAA4D", "#F9E547", "#8866BC")) +
    ggplot2::labs(
      title = "Performance Charges by OPS Group",
      subtitle = "Breakdown by month and standard grouping",
      caption = "Source: MOSL",
      fill = "OPS Group"
      ) +
    ggplot2::ylab("") + ggplot2::xlab("")
  }, error = function(e){}
)

```

<br>

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE}

# Creating table of charges by OPS ---------------- 

tryCatch(
  expr = {
  ops_data_clean_temp %>%
    dplyr::filter(
      Period >= data.period %m-% months(11),
      PerformanceMeasure == "Completed",
      Charges > 0
      ) %>%
    base::droplevels() %>%
    dplyr::select(Period, Standard, Charges) %>%
    dplyr::mutate(
      Period = format(Period, "%Y-%m"),
      Charges = tidyr::replace_na(Charges, 0)
      ) %>% 
    tidyr::drop_na(Charges) %>%
    base::droplevels() %>%
    tidyr::spread(Standard, Charges) %>%
    dplyr::mutate(Total = rowSums(dplyr::select(., -Period), na.rm = TRUE)) %>%
    dplyr::mutate_if(~ any(is.na(.)), ~ ifelse(is.na(.), 0, .)) %>%
    dplyr::mutate_if(is.numeric, scales::dollar_format(prefix = "£")) %>%
    tidyr::gather("Standard", "Charges", -Period) %>%
    tidyr::spread(Period, Charges) %>%
    kableExtra::kable (
      format = "latex", 
      caption = "Breakdown of Charges by Standard", 
      linesep = "",
      format.args = list(big.mark = ","),
      booktabs = TRUE,
      align = "c"
      ) %>%
    kableExtra::kable_styling(
      font_size = 10,
      latex_options = c(
        "repeat_header",
        "hold_position",
        "striped",
        position = "center", 
        full_width = FALSE,
        "scale_down"
        )
      ) %>%
    kableExtra::row_spec(0, bold = TRUE)
  }, error = function(e){}
)

```

## Performance Overview

As of `r format(data.period, "%B-%Y")`, MOSL were monitoring `r SHORT.NAME`'s performance against `r nrow(perf_status_ops_temp)` standards. The performance of Trading Parties against these standards is measured according to:

* `r paste(unique(perf_status_ops$PerformanceMeasure), collapse = " and ")`

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, fig.width = 12, fig.height = 5}

tryCatch(
  expr = {
  agg_perf <- ops_aggregate_perf %>%
    dplyr::filter(Trading.Party.ID == TRADING.PARTY) %>%
    dplyr::select(Period, PerformanceMeasure, Agg_Perf_roll) %>%
    dplyr::rename(GroupPerf = Agg_Perf_roll) %>%
    dplyr::mutate(Group = "Aggregate Performance")
  
  ops_data_clean_temp %>%
    dplyr::group_by(Period, PerformanceMeasure, Group) %>%
    dplyr::summarise(
      GroupPerf = stats::weighted.mean(Performance, TaskVolume)
      ) %>%
    dplyr::ungroup() %>%
    dplyr::group_by(PerformanceMeasure, Group) %>%
    dplyr::mutate(
      GroupPerf = zoo::rollapply(GroupPerf, 6, mean, align = "right", fill = NA)
      ) %>%
    dplyr::ungroup() %>%
    base::rbind(., agg_perf) %>%
    tidyr::drop_na(GroupPerf) %>%
    droplevels() %>%
    tidyr::drop_na() %>%
    ggplot2::ggplot() + 
    ggplot2::geom_line(
      ggplot2::aes(
        x = Period, 
        y = GroupPerf, 
        colour = Group,
        linetype = Group
        )
      ) +
    ggplot2::geom_point(
      ggplot2::aes(
        x = Period, 
        y = GroupPerf,
        colour = Group,
        fill = Group,
        shape = Group
        )
      ) +
    ggplot2::theme(
      legend.title = ggplot2::element_blank(),
      text = ggplot2::element_text(size = 15)
      ) +
    ggplot2::scale_y_continuous(
      labels = scales::percent_format(accuracy = 1),
      breaks = scales::pretty_breaks(4)
      ) +
    ggplot2::theme_bw() + 
    ggplot2::scale_colour_manual(
      values = c("#425563", "#05C3DE", "#005F83", "#00A499", "#FFAA4D", "#F9E547", "#8866BC")
      ) +
    ggplot2::scale_fill_manual(
      values = c("#425563", "#05C3DE", "#005F83", "#00A499", "#FFAA4D", "#F9E547", "#8866BC")
      ) +
    ggplot2::labs(
      title = paste0("Completed and Outstanding Tasks OPS Performance: ", SHORT.NAME),
      subtitle = "Breakdown by month and OPS standard grouping",
      caption = "Note: Aggregate performance corresponds to the 6-month average of aggregate OPS performance\nSource: MOSL"
      ) +
    ggplot2::ylab("") + ggplot2::xlab("") +
    ggplot2::facet_wrap(~PerformanceMeasure)
  }, error = function(e){}
)

```

<br>

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis"}

tryCatch(
  expr = {
  ops_data_clean_temp %>% 
    dplyr::filter(
      Period >= max(ops_data_clean_temp$Period) %m-% months(11),
      PerformanceMeasure == "Completed",
      TaskVolume > 0
      ) %>%
    tidyr::drop_na(TaskVolume) %>%
    base::droplevels() %>%
    dplyr::mutate(
      Performance = scales::percent(Performance, accuracy = 1),
      Period = format(Period, "%Y-%m")
      ) %>%
    dplyr::select(
      Period, Standard, Performance
      ) %>%
    tidyr::drop_na(Performance) %>%
    base::droplevels() %>%
    tidyr::spread(key = Period, value = Performance) %>%
    kableExtra::kable(
      format = "latex", 
      caption = "OPS On Time Completed Tasks by Month",
      linesep = "",
      format.args = list(big.mark = ","),
      booktabs = TRUE,
      align = "c"
      ) %>%
    kableExtra::kable_styling(
      font_size = 10,
      latex_options = c(
        "repeat_header",
        "hold_position",
        "striped",
        position = "center", 
        full_width = FALSE,
        "scale_down"
        )
      ) %>%
    kableExtra::row_spec(0, bold = TRUE)
  }, error = function(e){}
)

```

<br>

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis"}

tryCatch(
  expr = {
  ops_data_clean_temp %>% 
    dplyr::filter(
      Period >= max(ops_data_clean_temp$Period) %m-% months(11),
      PerformanceMeasure == "Outstanding",
      TaskVolume > 0
      ) %>%
    tidyr::drop_na(TaskVolume) %>%
    base::droplevels() %>%
    dplyr::mutate(
      Performance = scales::percent(Performance, accuracy = 1),
      Period = format(Period, "%Y-%m")
      ) %>%
    dplyr::select(
      Period, Standard, Performance
      ) %>%
    tidyr::drop_na(Performance) %>%
    base::droplevels() %>%
    tidyr::spread(key = Period, value = Performance) %>%
    kableExtra::kable(
      format = "latex", 
      caption = "OPS Outstanding Tasks Within Time by Month",
      linesep = "",
      format.args = list(big.mark = ","),
      booktabs = TRUE,
      align = "c"
      ) %>%
    kableExtra::kable_styling(
      font_size = 10,
      latex_options = c(
        "repeat_header",
        "hold_position",
        "striped",
        position = "center", 
        full_width = FALSE,
        "scale_down"
        )
      ) %>%
    kableExtra::row_spec(0, bold = TRUE)
  }, error = function(e){}
)

```

`r SHORT.NAME`'s 6-month average aggregate OPS performance for completed tasks is `r scales::percent(ops_aggregate_perf_temp$Agg_Perf_roll[ops_aggregate_perf_temp$PerformanceMeasure == "Completed"], accuracy = 1)`, which currently ranks as:

* `r scales::ordinal(ops_aggregate_perf_temp$rank_all[ops_aggregate_perf_temp$PerformanceMeasure == "Completed"])` out of `r ops_aggregate_perf_temp$n_all[ops_aggregate_perf_temp$PerformanceMeasure == "Completed"]` for all Trading Parties
* `r scales::ordinal(ops_aggregate_perf_temp$rank_type[ops_aggregate_perf_temp$PerformanceMeasure == "Completed"])` out of `r paste0(ops_aggregate_perf_temp$n_type[ops_aggregate_perf_temp$PerformanceMeasure == "Completed"], " ", ops_aggregate_perf_temp$tp_type[ops_aggregate_perf_temp$PerformanceMeasure == "Completed"])`s
* `r scales::ordinal(ops_aggregate_perf_temp$rank_subtype[ops_aggregate_perf_temp$PerformanceMeasure == "Completed"])` out of `r ops_aggregate_perf_temp$n_subtype[ops_aggregate_perf_temp$PerformanceMeasure == "Completed"]` trading parties with licence type `r ops_aggregate_perf_temp$sub_type[ops_aggregate_perf_temp$PerformanceMeasure == "Completed"]`

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, fig.width = 12, fig.height = 6}

tryCatch(
  expr = {
  ops_aggregate_perf %>%
    dplyr::filter(
      sub_type == as.character(ops_aggregate_perf_temp$sub_type),
      Period == data.period,
      PerformanceMeasure == "Completed"
      ) %>%
    ggplot2::ggplot() +
    ggplot2::geom_bar(
      ggplot2::aes(
        x = reorder(ShortName, Agg_Perf_roll), 
        y = Agg_Perf_roll,
        fill = dplyr::if_else(Trading.Party.ID == TRADING.PARTY, "highlight", "normal")
        ), 
      stat = "identity",
      show.legend = FALSE) +
    ggplot2::scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    ggplot2::scale_fill_manual(values = c("#425563", "azure3")) +
    ggplot2::coord_flip() +
    ggplot2::theme_bw() + 
    ggplot2::theme(
      text = ggplot2::element_text(size = 15)
      ) +
    ggplot2::labs(
      title = "Ranking of Overall OPS Performance (Completed)",
      subtitle = 
        paste0(
          "Rolling 6-month mean of aggregate OPS performance by Trading Party (", 
          ops_aggregate_perf_temp$sub_type, ")"
          ),
      caption = "Source: MOSL"
      ) +
    ggplot2::ylab("") + ggplot2::xlab("")
  }, error = function(e){}
)

```

`r SHORT.NAME`'s 6-month average aggregate OPS performance for outstanding tasks is `r scales::percent(ops_aggregate_perf_temp$Agg_Perf_roll[ops_aggregate_perf_temp$PerformanceMeasure == "Outstanding"], accuracy = 1)`, which currently ranks as:

* `r scales::ordinal(ops_aggregate_perf_temp$rank_all[ops_aggregate_perf_temp$PerformanceMeasure == "Outstanding"])` out of `r ops_aggregate_perf_temp$n_all[ops_aggregate_perf_temp$PerformanceMeasure == "Outstanding"]` for all Trading Parties
* `r scales::ordinal(ops_aggregate_perf_temp$rank_type[ops_aggregate_perf_temp$PerformanceMeasure == "Outstanding"])` out of `r paste0(ops_aggregate_perf_temp$n_type[ops_aggregate_perf_temp$PerformanceMeasure == "Outstanding"], " ", ops_aggregate_perf_temp$tp_type[ops_aggregate_perf_temp$PerformanceMeasure == "Outstanding"])`s
* `r scales::ordinal(ops_aggregate_perf_temp$rank_subtype[ops_aggregate_perf_temp$PerformanceMeasure == "Outstanding"])` out of `r ops_aggregate_perf_temp$n_subtype[ops_aggregate_perf_temp$PerformanceMeasure == "Outstanding"]` trading parties with licence type `r ops_aggregate_perf_temp$sub_type[ops_aggregate_perf_temp$PerformanceMeasure == "Outstanding"]`

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, fig.width = 12, fig.height = 6}

tryCatch(
  expr = {
  ops_aggregate_perf %>%
    dplyr::filter(
      sub_type == as.character(ops_aggregate_perf_temp$sub_type),
      Period == data.period,
      PerformanceMeasure == "Outstanding"
      ) %>%
    ggplot2::ggplot() +
    ggplot2::geom_bar(
      ggplot2::aes(
        x = reorder(ShortName, Agg_Perf_roll), 
        y = Agg_Perf_roll,
        fill = dplyr::if_else(Trading.Party.ID == TRADING.PARTY, "highlight", "normal")
        ), 
      stat = "identity",
      show.legend = FALSE) +
    ggplot2::scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    ggplot2::scale_fill_manual(values = c("#425563", "azure3")) +
    ggplot2::coord_flip() +
    ggplot2::theme_bw() + 
    ggplot2::theme(
      text = ggplot2::element_text(size = 15)
      ) +
    ggplot2::labs(
      title = "Ranking of Overall OPS Performance (Outstanding)",
      subtitle = 
        paste0(
          "Rolling 6-month mean of aggregate OPS performance by Trading Party (", 
          ops_aggregate_perf_temp$sub_type, ")"
          ),
      caption = "Source: MOSL"
      ) +
    ggplot2::ylab("") + ggplot2::xlab("")
  }, error = function(e){}
)

```

The current status of `r SHORT.NAME`'s performance against each standard and performance measure is summarised in the table(s) below: 

``` {r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis"}

for (MEASURE in unique(perf_status_ops_temp$PerformanceMeasure)) {

  tryCatch(
  expr = {
    perf_status_ops_temp %>%
      dplyr::filter(
        PerformanceMeasure == MEASURE
        ) %>%
      dplyr::select(
        Standard, SecondaryCategory, Consistency, PerfRating, Status, Action
        ) %>%
      dplyr::mutate(
        Status = tidyr::replace_na(Status, "")
        ) %>%
      kableExtra::kable(
        format = "latex", 
        caption = paste0("Current Status of OPS (", MEASURE, ")"),
        linesep = "",
        booktabs = TRUE,
        col.names = c("OPS", "Category", "Performance Consistency", "Performance Rating", "IPRP Status", "MOSL Action"),
        align = c("llcccc")
        ) %>%
      kableExtra::column_spec(3:4, width = "3.5cm") %>%
      kableExtra::kable_styling(
        latex_options = c(
          "repeat_header",
          "HOLD_position",
          "striped",
          position = "center", 
          full_width = FALSE,
          "scale_down"
          )
        ) %>%
      kableExtra::row_spec(0, bold = TRUE) %>%
      print()
    
    cat("\n")
  }, error = function(e){}
  )

}

```

<br>

See Appendix for an explanation of how MOSL rates Trading Party performance and consistency against the standards.

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, fig.width = 12, fig.height = 6}

tryCatch(
  expr = {
  perf_status_ops_temp %>%
    ggplot2::ggplot() +
    ggrepel::geom_label_repel(
      ggplot2::aes(
        x = rolling.sd,
        y = rolling.mean,
        label = Standard,
        fill= Group
        ), alpha = 0.8
      ) +
    ggplot2::scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    ggplot2::scale_x_reverse(labels = scales::percent_format(accuracy = 1)) +
    ggplot2::theme_bw() +
    ggplot2::scale_fill_manual(
      values = c("#425563", "#05C3DE", "#005F83", "#00A499", "#FFAA4D", "#F9E547", "#8866BC")
      ) +
    ggplot2::theme(
      text = ggplot2::element_text(size = 15)
      ) +
    ggplot2::labs(
      title = paste0("OPS Performance Rating and Consistency as of ", format(as.Date(data.period), '%B %Y')),
      subtitle = "Rolling 6-month mean and standard deviation of OPS performance",
      caption = "Source: MOSL"
      ) +
    ggplot2::ylab("Performance") + ggplot2::xlab("Consistency") +
    ggplot2::facet_wrap(~ PerformanceMeasure)
  }, error = function(e){}
)
    
```

## Detailed Analysis

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis"}

ops_list <- levels(droplevels(perf_status_ops$Standard[perf_status_ops$Trading.Party.ID == TRADING.PARTY & perf_status_ops$TaskVolume > 0]))

res <- lapply(ops_list, function (OPS_CHUNK) {
  
  knitr::knit_child(
    "pfm_report_ops_template.Rmd", envir = environment(), quiet = TRUE
    )
  }
  )

cat(unlist(res), sep = "\n")

```
 
<br>

## Market Aggregates

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis"}

metrics.list <- c("MarketMean", "MarketMedian", "MarketTaskVolume")

for (METRIC in metrics.list) {

  for (MEASURE in unique(ops_summary$PerformanceMeasure)) {
  
    ops_summary %>% 
      dplyr::filter(
        PerformanceMeasure == MEASURE
        ) %>%
      tidyr::drop_na() %>%
      dplyr::select(
        Period, Standard, METRIC
        ) %>% 
      dplyr::filter(
        Period >= data.period %m-% months(11)
        ) %>% 
      dplyr::mutate(Period = format(Period, "%Y-%m")) %>%
      tidyr::spread(Period, METRIC) %>%
      dplyr::mutate_if(
        is.numeric, 
        ifelse(
          METRIC != "MarketTaskVolume", 
          scales::percent_format(accuracy = 1), 
          scales::number_format(big.mark = ",", accuracy = 1)
          )
        ) %>%
      kableExtra::kable(
        format = "latex", 
        caption = paste0("Market ", base::gsub("_", x = METRIC, replacement = " "), " (", MEASURE, ")"), 
        linesep = "",
        digits = 1,
        booktabs = TRUE,
        align = "c"
        ) %>%
      kableExtra::kable_styling(
        latex_options = c(
          "repeat_header",
          "HOLD_position",
          "striped",
          "scale_down"
          )
        ) %>%
      kableExtra::row_spec(0, bold = TRUE) %>%
      print()
    
    cat("\n")
    
  }
  
}

```
