### `r paste0(OPS_CHUNK, ": ", OPS_details$Context[OPS_details$OPS == OPS_CHUNK])`

> `r OPS_details$Details[OPS_details$OPS == OPS_CHUNK]`

`r SHORT.NAME`'s on-time task performance for `r OPS_CHUNK`  is rated as 

* `r paste0(perf_status_ops_temp$Consistency[perf_status_ops_temp$OPS == OPS_CHUNK], ", ", perf_status_ops_temp$PerfRating[perf_status_ops_temp$OPS == OPS_CHUNK])`

Below is a graph showing `r SHORT.NAME`'s historical on-time task completion performance for `r OPS_CHUNK`. MOSL action points and IPRP milestones are shown, if applicable. 

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, fig.width = 12, fig.height = 5}

on.iprp <- perf_status_ops_temp$IPRP[perf_status_ops_temp$OPS == OPS_CHUNK]

graph <- perf_status_ops %>%
  dplyr::filter(
    TaskVolume > 0
    ) %>%
  MOSLR::ops_plot_perf_graph(
    data = ., 
    load.data = FALSE,
    melt.data = TRUE,
    Standard = OPS_CHUNK,
    TradParty = TRADING.PARTY,
    filter.date.from = data.period %m-% months(11),
    filter.date.to = data.period, 
    action.points = TRUE,
    include.iprp = on.iprp,
    graph.title = OPS_CHUNK,
    sub.title = OPS_details$Context[OPS_details$OPS == OPS_CHUNK],
    x.lab = "Performance"
    ) +
  ggplot2::theme(
    text = ggplot2::element_text(size = 15)
  )

tryCatch(
  expr = {
    plot(graph)
    },
  error = function(e){
    message("Error printing OPS performance graph")
    print(e)
  }
  )

```

`r OPS_CHUNK` has had:

* `r perf_status_ops_temp$SumPerf3m[perf_status_ops_temp$OPS == OPS_CHUNK]` performance flags
* `r perf_status_ops_temp$CumWatch[perf_status_ops_temp$OPS == OPS_CHUNK]` watch flags

`r if (on.iprp) { paste0(OPS_CHUNK, " is currently on an IPRP. See below for further details.") } else { paste0(OPS_CHUNK, " is not on an IPRP.") }`

<br> 

```{r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE} 

RATIONALE_CHUNK <- nrow(perf_status_ops %>% dplyr::filter(Trading.Party.ID == TRADING.PARTY, OPS == OPS_CHUNK, Action != "")) > 0

PFM_COMM_CHUNK <- nrow(perf_status_ops %>% dplyr::filter(Trading.Party.ID == TRADING.PARTY, OPS == OPS_CHUNK, !is.na(PFM_Commentary), PFM_Commentary != "")) > 0

```

`r if (RATIONALE_CHUNK) { paste0("The table below shows the rationale for MOSL actions regarding ",  paste0(OPS_CHUNK), ".") }`

``` {r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis", eval = RATIONALE_CHUNK}

perf_status_ops %>%
  dplyr::filter(
    Trading.Party.ID == TRADING.PARTY,
    OPS == OPS_CHUNK,
    Action != ""
    ) %>%
  dplyr::select(
    Date, Action, Rationale
    ) %>%
  dplyr::mutate(
    Date = format(Date, "%Y-%m")
    ) %>%
  kableExtra::kable(
    format = "latex", 
    caption = "Rationale for Recent MOSL Actions",
    linesep = "",
    longtable = TRUE, 
    booktabs = TRUE
    ) %>%
  kableExtra::column_spec(3, width = "10cm") %>%
  kableExtra::kable_styling(
    font_size = 10,
    latex_options = c(
      "repeat_header",
      "hold_position",
      #full_width = TRUE,
      "striped"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)

```

<br> 

`r if (PFM_COMM_CHUNK) { paste0("The table below shows the commentary MOSL has received from Portfolio Managers regarding ",  paste0(OPS_CHUNK), ".") }`

``` {r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis", eval = PFM_COMM_CHUNK}

perf_status_ops %>%
  dplyr::filter(
    Trading.Party.ID == TRADING.PARTY,
    OPS == OPS_CHUNK,
    !is.na(PFM_Commentary), 
    PFM_Commentary != ""
    ) %>%
  dplyr::select(
    Date, PFM_Commentary
    ) %>%
  dplyr::mutate(
    Date = format(Date, "%Y-%m")
    ) %>%
  kableExtra::kable(
    format = "latex", 
    caption = "Rationale for Recent MOSL Actions",
    linesep = "",
    longtable = TRUE, 
    booktabs = TRUE,
    col.names = c("Date", "Portfolio Manager Commentary")
    ) %>%
  kableExtra::column_spec(2, width = "12cm") %>%
  kableExtra::kable_styling(
    font_size = 10,
    latex_options = c(
      "repeat_header",
      "hold_position",
      "striped"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)

```

<br> 

`r if (on.iprp) { paste0("A summary of ", SHORT.NAME, "'s performance against its IPRP is shown in the table below.") }`

``` {r message = FALSE, echo = FALSE, error = FALSE, warning = FALSE, results = "asis", eval = on.iprp}

perf_status_ops %>%
  dplyr::filter(
    Trading.Party.ID == TRADING.PARTY,
    OPS == OPS_CHUNK,
    ) %>%
  dplyr::select(
    Date, TaskCompletion, Planned_Perf, DeltaQuant, Status
    ) %>%
  tidyr::drop_na() %>%
  dplyr::mutate(
    Date = format(Date, "%Y-%m"),
    TaskCompletion = format(TaskCompletion, digits = 2),
    DeltaQuant = format(DeltaQuant * 100, digits = 2)
    ) %>%
  kableExtra::kable(
    format = "latex", 
    caption = "IPRP Performance Tracking",
    linesep = "",
    longtable = TRUE, 
    booktabs = TRUE,
    col.names = c("Date", "Actual Performance", "Planned Performance", "Difference (%)", "IPRP Status"),
    align = rep("c", 5)
    ) %>%
  kableExtra::column_spec(1:5, width = "2.5cm") %>%
  kableExtra::kable_styling(
    font_size = 10,
    latex_options = c(
      "repeat_header",
      "hold_position",
      "striped"
      )
    ) %>%
  kableExtra::row_spec(0, bold = TRUE)

```

<br> 

`r if (on.iprp) { paste0("For this plan there have been:") }`

`r if (on.iprp) { paste0("* ",  perf_status_ops_temp$CumResubmit[perf_status_ops_temp$OPS == OPS_CHUNK], " resubmission(s)") }`
`r if (on.iprp) { paste0("* ",  sum(perf_status_ops_temp$UnderReview[perf_status_ops_temp$OPS == OPS_CHUNK]), " review(s)") }`
